\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 prelims.tex
.

>>>>

\subsection{Bounded Model Checking (BMC)}
The PWA transition system is a finite location, infinite state
transition system. As all the guards and transitions are affine, a
bounded time reachability query is equivalent to checking all
combinaions of discrete locations, where each combination can be
summarized as a linear program. As the time is bounded, the number of
combinations are finite, although exponential in number.

It should be noted that an explicit execution of the transition system
represents a directed acyclic graph, with each location being a node,
and a directed edge (in the direction of time advance) from each node
to its reachable node. A path on this graph is then a linear program,
with each branching corresponsing to a logical disjunction.

Temporal properties of pwa transitions systems can be checked using
off-the-shelf model checkers like SAL~\cite{SAL-SRI} which can verify
infinite state transitions systems.  Furthermore, lazy SMT solvers can
be used for this specific problem~\cite{shoukry2017smc}. We now show
how relational pwa abstractions can be viewed as pwa transition
systems and subsequenly, the problem of falsification can be answered
by a BMC query.
